Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s07_problempinning.tex
Corrected a figure
White space fixes.
Adding some citations
Added citations

\section{Application: Finding completions of under-constrained glassy structures to isostatic}
\label{sec:bodypin}

We can use DR-plans to help in solving questions in designs for graphene and silica bi-layers \uncited. Specifically, we will look into the problem when you have a mono-layer and it is under-constrained. Our goal is to make such a layer isostatic. This can be done in a number of ways.

\begin{figure}\centering
    \includegraphics[width=0.4\linewidth]{img/Silica} \hspace{0.5cm}
    \raisebox{0.3\height}{\includegraphics[width=0.2\linewidth]{img/Silicon_tetrahedron}}
    \caption{Example of a single mono-layer of a Silica Oxygen glassy structure. This can be thought of as a multi-triangle-pin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins. Not shown here are other layers stacked on this one. Each Silicon atom has the structure seen to the right, and so binds to another Oxygen atom in an adjacent mono-layer.}
    \label{fig:silica_glass}
\end{figure}

@@

    (b)
    \begin{subfigure}{0.8\linewidth}
        \includegraphics[width=\linewidth]{img/pentawesome}
    \end{subfigure}
    \caption{Examples of self-similarity in the form of repeated subdivision. In (a), a simple subdivision is done that does not guarantee isostatic. In (b), a more complicated scheme is used, ensuring that the resulting graph is both isostatic and non-tree-decomposable.}
    \label{fig:subdivision}
\end{figure}

@@

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.3\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}

>>>>

\section{Application: Finding completions of under-constrained glassy structures to isostatic}
\label{sec:bodypin}
% \bibliography{paper}

We can use DR-plans to help in solving questions in designs for graphene and silica bi-layers \cite{silica_bilayers} \cite{sructure_of_2d_glass}. Specifically, we will look into the problem when you have a mono-layer and it is under-constrained. Our goal is to make such a layer isostatic. This can be done in a number of ways.

\begin{figure}\centering
    \includegraphics[width=0.4\linewidth]{img/Silica} \hspace{0.5cm}
    \raisebox{0.3\height}{\includegraphics[width=0.2\linewidth]{img/Silicon_tetrahedron}}
    \caption{Example of a single mono-layer of a Silica Oxygen glassy structure. This can be thought of as a multi-triangle-pin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins. Not shown here are other layers stacked on this one. Each Silicon atom has the structure seen to the right, and so binds to another Oxygen atom in an adjacent mono-layer. Pictures taken from \cite{silica_figure} and \cite{tetra_silica_figure}.}
    \label{fig:silica_glass}
\end{figure}

@@

    (b)
    \begin{subfigure}{0.8\linewidth}
        \includegraphics[width=\linewidth]{img/pentawesome}
    \end{subfigure}
    \caption{Examples of self-similarity in the form of repeated subdivision. In (a), a simple subdivision is done that does not guarantee isostatic. In (b), a more complicated scheme is used, ensuring that the resulting graph is both isostatic and non-tree-decomposable. Credit to \cite{subdivision_paper} for (a).}
    \label{fig:subdivision}
\end{figure}

@@

\begin{figure*}\centering
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \input{img/tikz/bodypin_graph.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.35\linewidth}\centering\scriptsize
    \input{img/tikz/bodypin_drp.tikz}
    \caption{}
\end{subfigure}
%
\begin{subfigure}{0.2\linewidth}\centering
    \includegraphics[width=\linewidth]{img/bodypin2}
    \caption{}
\end{subfigure}
%
\caption{(a) is a 1-dof body-pin graph. (b) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (c) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (d) is the result of adding one such body to the bold-faced node.}
